Análise de Complexidade e Experimental de Algoritmos de Ordenação

### 2018-04-23 Article/article.tex
Primeiros graficos

@@

>>>>

\centering
\pgfplotstableread{plots/aleatorio.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[legend style={at={(0.5,-0.1)},anchor=north}]
%\addplot [black,very thick] table [x={n}, y={bubble-class}] {\pistonkinetics};
%\addlegendentry{Bubble Sort}
%\addplot [red,very thick] table [x={n}, y={bubble-adv}] {\pistonkinetics};
%\addlegendentry{Bubble Sort Avançado}
\addplot [blue,very thick] table [x={n}, y={quick-inicial}] {\pistonkinetics};
\addlegendentry{Quick Sort Inicial}
\addplot [green,very thick] table [x={n}, y={quick-central}] {\pistonkinetics};
\addlegendentry{Quick Sort Central}
\addplot [yellow,very thick] table [x={n}, y={insertion}] {\pistonkinetics};
\addlegendentry{Insertion Sort}
\addplot [gray,very thick] table [x={n}, y={shell}] {\pistonkinetics};
\addlegendentry{Shell Sort}
\addplot [brown,very thick] table [x={n}, y={selection}] {\pistonkinetics};
\addlegendentry{Selection Sort}
\addplot [pink,very thick] table [x={n}, y={merge}] {\pistonkinetics};
\addlegendentry{Merge Sort}
\addplot [orange,very thick] table [x={n}, y={heap}] {\pistonkinetics};
\addlegendentry{Heap Sort}
\end{axis}
\end{tikzpicture}

@@

\centering
\pgfplotstableread{plots/bubble-sort.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[minor tick num=1,
xlabel=n elementos]
\addplot [black,very thick] table [x={n}, y={ale}] {\pistonkinetics};
\addplot [red,very thick] table [x={n}, y={cresc}] {\pistonkinetics};
\addplot [blue,very thick] table [x={n}, y={desc}] {\pistonkinetics};
\end{axis}
\end{tikzpicture}

\pgfplotstableread{plots/bubble-sort-adv.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[minor tick num=1,
xlabel=n elementos]
\addplot [black,very thick] table [x={n}, y={ale}] {\pistonkinetics};
\addplot [red,very thick] table [x={n}, y={cresc}] {\pistonkinetics};
\addplot [blue,very thick] table [x={n}, y={desc}] {\pistonkinetics};
\end{axis}
\end{tikzpicture}

\pgfplotstableread{plots/quick-sort-pivo-inicial.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[minor tick num=1,
xlabel=n elementos]
\addplot [black,very thick] table [x={n}, y={ale}] {\pistonkinetics};
\addplot [red,very thick] table [x={n}, y={cresc}] {\pistonkinetics};
\addplot [blue,very thick] table [x={n}, y={desc}] {\pistonkinetics};
\end{axis}
\end{tikzpicture}

\pgfplotstableread{plots/quick-sort-pivo-central.dat}{\pistonkinetics}
\begin{tikzpicture}[scale=1]
\begin{axis}[minor tick num=1,
xlabel=n elementos]
\addplot [black,very thick] table [x={n}, y={ale}] {\pistonkinetics};
\addplot [red,very thick] table [x={n}, y={cresc}] {\pistonkinetics};
\addplot [blue,very thick] table [x={n}, y={desc}] {\pistonkinetics};
\end{axis}
\end{tikzpicture}
